\section{Introduction}

In modern information systems, knowledge is gathered from large quantities of various sources. These systems form the basis of various tools that we use today, ranging from search engines and knowledge bases to recommendation systems and scientific databases. One of the largest repositories of information used by these systems is the web. The information that is available on the web is published by millions of independent sources, all with varying levels of expertise and accuracy. This frequently leads to different descriptions provided by different sources referring to the same underlying entities.

Determining which of these descriptions should be trusted is often far from being straightforward. Some inconsistencies can be due to errors or outdated information, whereas others may be attributed to misinterpretation, incomplete information, or perhaps information that has otherwise been propagated across several sources. To validate information, they typically rely on external evidence such as referencing authoritative sources or using human judgment. These approaches are effective if reliable external evidence is accessible, but they need to be constantly maintained and ultimately rely on the availability of trusted sources.

With recent advancements in artificial intelligence systems, particularly, large language models (LLMs) and autonomous agents, these problems are amplified even further. An agent is likely to browse the web to gather information from multiple sources and use the result to make decisions and execute downstream tasks autonomously. Given the rapid rate at which these systems retrieve and distribute such information, referring to external evidence constantly for every decision is slow, computationally expensive, and cannot keep pace with the scale at which autonomous agents operate.

In this paper, we present Verity, a graph-based framework for inferring source credibility in large collections of conflicting claims. It estimates source credibility from the network of assertions connecting sources and claims. These credibility estimates allow agents to distinguish between conflicting descriptions while avoiding reliance on external evidence.
